### 2013-07-16 Tex/chapters/results.tex
nu durch Mittelung bestimmt, und etwas ausführlicher beschrieben

    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.

@@

    using \texttt{autoscale.py} \cite{autoscale2009}. The values for

@@

    \(\sigma\), the steep decline and the shallow decline at \(\sigma = 0.5\).\\

@@

            Gabriel      & 0.0 & 1.008(4) & -1.735(2) & 0.1262(4)\\
                         & 0.1 & 1.02(1)  & -1.744(5) & 0.133(6) \\
                         & 0.3 & 1.000(5) & -1.724(16)& 0.129(12)\\
                         & 0.5 & 1.009(8) & -1.750(12)& 0.125(13)\\
                         & 1.0 & 1.015(22)& -1.743(17)& 0.123(16)\\

@@

            Relative N.  & 0.0 & 1.007(2) & -1.740(2) & 0.130(1) \\
                         & 0.1 & 0.99(1)  & -1.746(5) & 0.133(4) \\
                         & 0.2 & 1.022(17)& -1.756(14)& 0.123(10)\\
                         & 0.5 & 1.002(17)& -1.750(16)& 0.143(13)\\
                         & 1.0 & 1.011(20)& -1.758(16)& 0.138(13)\\

>>>>

    collapse in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}%\footnote{Examples for a collapse to determine the other critical exponents are in appendix \ref{appendix:finiteSizeScaling}}.

@@

    using \texttt{autoscale.py} \cite{autoscale2009} and eq. \eqref{eq:fsscaling:m}-\eqref{eq:fsscaling:g}.
    The values for \(\nu\) are yielded by every collapse and are therefore
    averaged over all determined values. Fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_sus}\subref{sfig:gettingCrit:collapse_s_0_sus}
    show an example collapse for \(\sigma=0\) of the magnetic susceptibility
    \[\chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}\]
    This way the exponents \(\gamma\) and \(\nu\) are determined.
    Analogical fig. \ref{fig:gettingCrit2}\subref{sfig:gettingCrit:s_0_meanM}\subref{sfig:gettingCrit:collapse_s_0_meanM}
    shows the collapse for the mean absolute magnetisation per site \(\avg{\abs{m}}\) for \(\sigma=0\),
    to determine the exponents \(\beta\) and \(\nu\).
    Also the collapse of the binder cumulant as mentioned before and shown
    in fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
    is used to get a further value of \(\nu\).
        \subfigure[Susceptibility $\chi$][]
            \label{sfig:gettingCrit:s_0_sus}
            \includegraphics[width=0.47\textwidth]{plots/s_0_sus}
        \subfigure[Finite Size Scaling of the Susceptibility $\chi$][]
            \label{sfig:gettingCrit:collapse_s_0_sus}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_sus}
        \subfigure[Magnetisation $\avg{\abs{m}}$][]
            \label{sfig:gettingCrit:s_0_meanM}
            \includegraphics[width=0.47\textwidth]{plots/s_0_meanM}
        \subfigure[Finite Size Scaling of the Magnetisation $\avg{\abs{m}}$][]
            \label{sfig:gettingCrit:collapse_s_0_meanM}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_meanM}
            Examples for finite size scaling.
        \label{fig:gettingCrit2}
    The values for

@@

    \(\sigma\), the steep decline and the shallow decline at \(\sigma = 0.5\).
    The given errors for \(\beta, \gamma\) are estimates from \texttt{autoscale.py}
    and the error of \(\nu\) is the standard deviation of the three obtained
    values of \(\nu\).\\

@@

            Gabriel      & 0.0 & 0.998(8) & -1.735(2) & 0.1262(4)\\
                         & 0.1 & 0.999(19)& -1.744(5) & 0.133(6) \\
                         & 0.3 & 1.029(30)& -1.724(16)& 0.129(12)\\
                         & 0.5 & 1.006(5) & -1.750(12)& 0.125(13)\\
                         & 1.0 & 1.038(32)& -1.743(17)& 0.123(16)\\

@@

            Relative N.  & 0.0 & 0.992(11)& -1.740(2) & 0.130(1) \\
                         & 0.1 & 0.987(12)& -1.746(5) & 0.133(4) \\
                         & 0.2 & 1.010(9) & -1.756(14)& 0.123(10)\\
                         & 0.5 & 1.010(16)& -1.750(16)& 0.143(13)\\
                         & 1.0 & 1.013(6) & -1.758(16)& 0.138(13)\\
